Investigating country-level activity and mobility patterns and their interdependencies on COVID-19 outcomes

### 2020-12-03 docs/manuscript/manuscript.tex
Updated data sources and variables

\begin{table}[h!]\small
  \centering
  \caption{Summary of data sources}
  \label{tab:sources}
\begin{tabular}{ll}\toprule
\bf Source                         & \bf Overview                                                                              \\\midrule
Johns Hopkins University          & Time series summary globally.                                                               \\
Apple Maps                        & Compared to a baseline volume on January 13th, 2020.                                          \\
  Google Community Mobility Reports & Compared to a baseline day \\
  & (median value over period from Jan 3 to Feb 6, 2020)\\\bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
  \centering
\caption{Summary of variables}
\label{tab:variables}
\small
\begin{tabular}{ll}\toprule
\textbf{Variable}                                         & \textbf{Description}                                    \\\midrule
confirmed\_cases                                         & Newly confirmed cases of COVID-19              \\
driving                                                  & Requests for driving directions in Apple Maps.    \\
walking                                                  & Requests for walking directions in Apple Maps   \\
transit                                                  & Requests for transit directions in Apple Maps   \\
retail\_and\_recreation\_percent\_change\_from\_baseline & Retail and recreation movement trends.            \\
grocery\_and\_pharmacy\_percent\_change\_from\_baseline  & Grocery and pharmacy movement trends.             \\
parks\_percent\_change\_from\_baseline                   & Parks movement trends.                           \\
transit\_stations\_percent\_change\_from\_baseline       & Transit stations movement trends.                \\
workplaces\_percent\_change\_from\_baseline              & Workplaces movement trends.                      \\
residential\_percent\_change\_from\_baseline             & Retail and recreation movement trends.          \\\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]\small
  \centering
  \caption{Summary of data sources}
  \label{tab:sources}
\begin{tabular}{ll}\toprule
\bf Source                         		         & \bf Overview                                                                              \\\midrule
Johns Hopkins University          	         & New COVID cases and COVID-related deaths \\
  & (global time series summary)                                                              \\
Google Community Mobility Reports      & Change in traffic compared to a baseline day \\
  & (median value over period from Jan 3 to Feb 6, 2020) 			\\
World Data Indicators 		         & Economic indicators (growth, GDP) \\
Government Measures		         & ACAPS Government Measures Dataset \\\bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
  \centering
\caption{Summary of variables}
\label{tab:variables}
\small
\begin{tabular}{ll}\toprule
\textbf{Variable}                                  & \textbf{Description}                                    \\\midrule
cases                                                    & New COVID cases tracked by JHU              \\
deaths                                                  & COVID-related deaths tracked by JHU    \\
grocery                                                 & Grocery and pharmacy activity percent change from baseline   \\
parks                                                     & Parks percent change from baseline   \\
transit                                                   & Transit stations activity percent change from baseline            \\
work					        & Workplaces activity percent change from baseline             \\
home				                   & Residential activity percent change from baseline                           \\
retail					        & Retail and recreation activity percent change from baseline                \\
pop				                   & Population                      \\
gdppc					         & GDP Per Capita		\\
growth				         & Growth			\\
pop\_den				         & Population Density 	\\
pop\_urb				         & Urban Population		\\
pop0\_14				         & Population Ages 0 to 14   \\
workpop				         & Working population (Ages 15-64) \\
pub\_health				         & Government Measures - Public Health  \\
soc\_econ				         & Government Measures - Socio-economic  \\
soc\_dist				         & Government Measures - Social Distancing  \\
mov\_rest				         & Government Measures - Movement Restrictions \\
lockdown				         & Government Measures - Lockdown  \\	
human				         & Government Measures - Humanitarian Exemption         \\\bottomrule
\end{tabular}
\end{table}
